Variance reduction for MCMC methods via martingale representations

### 2020-03-25 aap/Revision/vr-mcmc-revision-new-new.tex
update

Now we shall show that conditions {\bf (H1)} and {\bf (H2)} are sufficient to show that ULA kernel $Q_\gamma$ satisfies the drift condition \eqref{eq:drift}

>>>>

Now we shall show that conditions {\bf (H1)} and {\bf (H2)} are sufficient to show that ULA kernel $Q_\gamma$ satisfies the drift condition \eqref{eq:lyapunov}
